---
title: "CMPUT 664 - Project"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  
library("dplyr")
library("tidyr")
library("ggplot2")
library("readr")
library("reshape2")
library("philentropy")
```

```{r data_setup, echo=FALSE, results="hide", include=FALSE}
data = read_csv("./dataframe.csv")

used_languages = c('Russian', 'Spanish', 'French', 'Turkish', 'German', 'Japanese', 'Polish', 'Italian', 'Catalan', 'Korean', 'Chinese', 'Portuguese', 'Greek', 'Thai', 'Swedish')

data <- data %>%
  filter(!grepl(error_type, 'S')) %>%
  filter(language %in% used_languages)

learners <- data %>%
  group_by(language, head) %>%
  summarize(count=n()) %>%
  group_by(language) %>%
  count()

data <- merge(data, learners, by='language') %>%
  rename(learners = n)
```

# Grouping error types and plotting top 5 error types
```{r error_groups_frequency}
errors_frequency <-
  data[!duplicated(data[,c("head","error_type")]),] %>%
  count(error_type)

errors_frequency <- errors_frequency %>%
  mutate(freq = n / sum(n))

errors_frequency <- errors_frequency[order(errors_frequency$freq),]
errors_frequency$error_type <- factor(errors_frequency$error_type, levels = errors_frequency$error_type[order(-errors_frequency$freq)])
errors_frequency %>%
    top_n(5, freq) %>%
    ggplot(aes(x = error_type, y = freq)) + 
    ggtitle("Error types distribution") +
    labs(x="Error type", y="Frequency") +
    geom_bar(stat = "identity", width = 0.35) +
    theme(axis.text.x = element_text())
```

# Plotting error types distribution by language
```{r error_groups_frequency_by_language}
errors_by_language <-
    data[!duplicated(data[,c("head","error_type")]),] %>%
    group_by(language, learners) %>%
    count(error_type) %>%
    mutate(freq = n / learners)

errors_by_language %>%
    group_by(language) %>%
    filter(freq > 0.82) %>%
    ggplot(aes(x = error_type, y = freq)) + 
    geom_point() +
    facet_wrap(~language, nrow=4, ncol=4) +
    scale_y_continuous(limits = c(0, 1)) +
    ggtitle("Error distribution among languages") +
    labs(x="Error type", y="Error frequency") +
    theme(axis.text.x = element_text(size=6, angle=90))
```

# Plotting top error types by language
```{r top_errors_by_language}
top_errors_by_language <- errors_by_language %>%
  filter(freq > 0.82) %>%
  group_by(language)

top_errors_by_language_distribution <- errors_by_language %>%
  filter(error_type %in% unique(top_errors_by_language$error_type))

ggplot(top_errors_by_language_distribution, aes(x = language, y = freq)) + 
    geom_point() +
    geom_point(data=top_errors_by_language, colour="red") +
    facet_wrap(~error_type, nrow=3, ncol=3) +
    scale_y_continuous(limits = c(0, 1)) +
    ggtitle("Most frequent error types") +
    labs(x="Language", y="Frequency within language") +
    theme(plot.title = element_text(size = 12, face = "bold")) +
    theme(axis.text.x = element_text(size=6, angle=45))
```

## POS TAGS

# Plotting most common wrong pos-tags for each language
```{r wrong_pos_tags_by_language}
filtered_data <- merge(data, top_errors_by_language, by=c('language', 'error_type'))

error_pos_tags_from_top_types_by_language <-
  data[!duplicated(data[,c("head","error_pos")]),] %>%
  group_by(language, learners) %>%
  count(error_pos) %>%
  mutate(freq = n / learners)

error_pos_tags_from_top_types_by_language %>%
    group_by(language) %>%
    top_n(2) %>%
    ggplot(aes(x = error_pos, y = freq)) + 
    geom_point() +
    facet_wrap(~language, nrow=4, ncol=4) +
    ggtitle("Error POS tag distribution among languages") +
    labs(x="Error POS", y="Error frequency") +
    theme(axis.text.x = element_text(size=6, angle=25))
```

# Plotting most common corrected pos-tags for each language
```{r correct_pos_tags_by_language}
correct_pos_tags_from_top_types_by_language <-
  data[!duplicated(data[,c("head","correct_pos")]),] %>%
  group_by(language, learners) %>%
  count(correct_pos) %>%
  mutate(freq = n / learners)

correct_pos_tags_from_top_types_by_language %>%
    group_by(language) %>%
    top_n(2) %>%
    ggplot(aes(x = correct_pos, y = freq)) + 
    geom_point() +
    facet_wrap(~language, nrow=4, ncol=4) +
    ggtitle("Correct POS tag distribution among languages") +
    labs(x="Correct POS", y="Frequency") +
    theme(axis.text.x = element_text(size=6, angle=25))
```

## BIGRAMS

# Plotting wrong part-of-speech bigrams distribution by language
```{r wrong_bigrams_by_language}
error_bigrams_by_language <-
    data[!duplicated(data[,c("head","error_bigram")]),] %>%
    group_by(language, learners) %>%
    count(error_bigram)

error_bigrams_by_language <- error_bigrams_by_language %>%
  group_by(language, learners) %>%
  mutate(freq = n / learners) 

error_bigrams_by_language %>%
    group_by(language) %>%
    top_n(2) %>%
    ggplot(aes(x = error_bigram, y = freq)) + 
    geom_point() +
    facet_wrap(~language, nrow=4, ncol=4) +
    ggtitle("Error bigram distribution among languages") +
    labs(x="Error bigram", y="Error frequency") +
    theme(axis.text.x = element_text(size=6, angle=25))
```

# Plotting most frequent corrected part-of-speech bigrams
```{r top_correct_bigrams}
correct_bigrams <- filtered_data %>%
    count(correct_bigram) %>%
    mutate(freq = nn / sum(nn))
  
correct_bigrams$correct_bigram <- factor(correct_bigrams$correct_bigram, levels = correct_bigrams$correct_bigram[order(-correct_bigrams$freq)])

correct_bigrams %>%
    top_n(5, freq) %>%
    ggplot(aes(x = correct_bigram, y = freq)) + 
    ggtitle("Top 5 corrected bigram") +
    labs(x="Corrected bigram", y="Frequency") +
    geom_bar(stat = "identity", width = 0.35) +
    theme(axis.text.x = element_text())
```

# Plotting corrected part-of-speech bigrams distribution by language
```{r correct_bigrams_by_language}
correct_bigrams_by_language <-
   data[!duplicated(data[,c("head","correct_bigram")]),] %>%
    group_by(language, learners) %>%
    count(correct_bigram) %>%
    mutate(freq = n / learners) 

correct_bigrams_by_language %>%
    group_by(language) %>%
    top_n(4) %>%
    ggplot(aes(x = correct_bigram, y = freq)) + 
    geom_point() +
    facet_wrap(~language, nrow=4, ncol=4) +
    scale_y_continuous(limits = c(0, 1)) +
    ggtitle("Corrected bigram distribution among languages") +
    labs(x="Correct bigram", y="Frequency") +
    theme(axis.text.x = element_text(size=6, angle=25))
```

# Plotting most frequent corrected part-of-speech bigrams by language
```{r}
top_correct_bigrams_by_language <- correct_bigrams_by_language %>%
  group_by(language) %>%
  top_n(1, freq)

top_correct_bigrams_distribution <- correct_bigrams_by_language %>%
  filter(correct_bigram %in% unique(top_correct_bigrams_by_language$correct_bigram))

ggplot(top_correct_bigrams_distribution, aes(x = language, y = freq)) + 
    geom_point() +
    geom_point(data=top_correct_bigrams_by_language, colour="red") +
    facet_wrap(~correct_bigram, nrow=3, ncol=3) +
    ggtitle("Corrected bigrams and their distributions over languages") +
    labs(x="Language", y="Frequency within language") +
    theme(plot.title = element_text(size = 12, face = "bold")) +
    theme(axis.text.x = element_text(size=6, angle=45))
```

## TRIGRAMS

# Most common wrong part-of-speech trigrams
```{r error_trigrams}
error_trigrams <- filtered_data %>%
    count(error_trigram) %>%
    mutate(freq = nn / sum(nn))
  
error_trigrams$error_trigram <- factor(error_trigrams$error_trigram, levels = error_trigrams$error_trigram[order(-error_trigrams$freq)])

error_trigrams %>%
    top_n(5, freq) %>%
    ggplot(aes(x = error_trigram, y = freq)) + 
    ggtitle("Top 5 error trigrams") +
    labs(x="Error trigram", y="Frequency") +
    geom_bar(stat = "identity", width = 0.35) +
    theme(axis.text.x = element_text())
```

# Most common corrected part-of-speech trigrams
```{r corrected_trigrams}
correct_trigrams <- filtered_data %>%
    count(correct_trigram) %>%
    mutate(freq = nn / sum(nn))
  
correct_trigrams$correct_trigram <- factor(correct_trigrams$correct_trigram, levels = correct_trigrams$correct_trigram[order(-correct_trigrams$freq)])

correct_trigrams %>%
    top_n(5, freq) %>%
    ggplot(aes(x = correct_trigram, y = freq)) + 
    ggtitle("Top 5 corrected trigrams") +
    labs(x="Corrected trigram", y="Frequency") +
    geom_bar(stat = "identity", width = 0.35) +
    theme(axis.text.x = element_text())
```

# Plotting wrong part-of-speech trigrams distribution by language
```{r wrong_trigrams_by_language}
error_trigrams_by_language <-
    data[!duplicated(data[,c("head","error_trigram")]),] %>%
    group_by(language, learners) %>%
    count(error_trigram)

error_trigrams_by_language <- error_trigrams_by_language %>%
  group_by(language, learners) %>%
  mutate(freq = n / learners) 

top_error_trigrams_by_language <- error_trigrams_by_language %>%
  group_by(language) %>%
  top_n(2)

error_trigrams_by_language %>%
    group_by(language) %>%
    top_n(2) %>%
    ggplot(aes(x = error_trigram, y = freq)) + 
    geom_point() +
    facet_wrap(~language, nrow=4, ncol=4) +
    scale_y_continuous(limits = c(0, 1)) +
    ggtitle("Error trigram distribution among languages") +
    labs(x="Error trigram", y="Error frequency") +
    theme(axis.text.x = element_text(size=6, angle=90))
```

# Plotting corrected part-of-speech trigrams distribution by language
```{r correct_trigrams_by_language}
correct_trigrams_by_language <-
    data[!duplicated(data[,c("head","correct_trigram")]),] %>%
    group_by(language, learners) %>%
    count(correct_trigram) 

correct_trigrams_by_language <- correct_trigrams_by_language %>%
  group_by(language, learners) %>%
  mutate(freq = n / learners)

correct_trigrams_by_language %>%
    group_by(language) %>%
    top_n(3) %>%
    ggplot(aes(x = correct_trigram, y = freq)) + 
    geom_point() +
    facet_wrap(~language, nrow=4, ncol=4) +
    ggtitle("Correct trigram distribution among languages") +
    labs(x="Correct trigram", y="Error frequency") +
    theme(axis.text.x = element_text(size=6, angle=90))
```

# Plotting most frequent corrected part-of-speech trigrams by language
```{r}
top_correct_trigrams_by_language <- correct_trigrams_by_language %>%
  group_by(language) %>%
  top_n(1)

top_correct_trigrams_distribution <- correct_trigrams_by_language %>%
  filter(correct_trigram %in% unique(top_correct_trigrams_by_language$correct_trigram))

ggplot(top_correct_trigrams_distribution, aes(x = language, y = freq)) + 
    geom_point() +
    geom_point(data=top_correct_trigrams_by_language, colour="red") +
    facet_wrap(~correct_trigram, nrow=3, ncol=3) +
    ggtitle("Corrected trigram and their distributions over languages") +
    labs(x="Language", y="Frequency within language") +
    theme(plot.title = element_text(size = 12, face = "bold")) +
    theme(axis.text.x = element_text(size=6, angle=60))
```

# Matrix of error distribution similarity
```{r distance_matrix, echo=FALSE, results="hide", include=FALSE}
m <- matrix(0, ncol = 212, nrow = 0)
distance_df <- data.frame(m)
names(distance_df) <- c("id", used_languages)

for (l in used_languages) {
  vector <- c(l)
  for (l2 in used_languages) {
    combined_df = rbind(errors_by_language[which(errors_by_language$language==l),]$freq, errors_by_language[which(errors_by_language$language==l2),]$freq)
    vector <- c(vector, zapsmall(distance(combined_df, method = "euclidean"), digits = 2))
  }
  supplemental_data_frame <- data.frame(t(vector));
  colnames(supplemental_data_frame) <- c("id", used_languages);
  supplemental_data_frame
  distance_df<-rbind(distance_df, supplemental_data_frame)
}
```